---
title: "Distributions"
subtitle: "Population vs Sampling"
format: 
  html:
    error: false
    message: false
    warning: false
    toc: true
    code-fold: true
    css: ../styles.css
    math: katex  
---




**Sampling Distributions**

Key points about modality and skewness in sampling distributions:

Modality:

- Unimodal: A sampling distribution with only one prominent peak.

- Bimodal: A sampling distribution with two distinct peaks.

- Multimodal: A sampling distribution with more than two peaks.

- Uniform: In a uniform distribution, every value within a specified range has an equal probability of occurring, creating a flat horizontal line when visualized on a graph.

Skewness:

- Positive Skewness (Right Skewed): The tail of the distribution extends further to the right side, meaning there are a few very high values compared to the majority of lower values.

- Negative Skewness (Left Skewed): The tail of the distribution extends further to the left side, indicating a few very low values compared to most higher values.

- Zero Skewness (Symmetrical): The distribution is balanced with the left and right sides mirroring each other. 



```{r}

library(ggplot2)

# Unimodal
ggplot(data.frame(x = rnorm(1000)), aes(x)) +
  geom_density(fill = "blue", alpha = 0.5) +
  ggtitle("Unimodal Distribution")

# Bimodal
ggplot(data.frame(x = c(rnorm(500, -2), rnorm(500, 2))), aes(x)) +
  geom_density(fill = "green", alpha = 0.5) +
  ggtitle("Bimodal Distribution")

# Multimodal
ggplot(data.frame(x = c(rnorm(300, -4), rnorm(300, 0), rnorm(300, 4))), aes(x)) +
  geom_density(fill = "purple", alpha = 0.5) +
  ggtitle("Multimodal Distribution")

# Uniform
ggplot(data.frame(x = runif(1000, -5, 5)), aes(x)) +
  geom_histogram(aes(y = ..density..), bins = 30, fill = "orange", color = "black", alpha = 0.5) +
  ggtitle("Uniform Distribution")


```





```{r}

# Positive Skew
ggplot(data.frame(x = rexp(1000, rate = 1)), aes(x)) +
  geom_density(fill = "red", alpha = 0.5) +
  ggtitle("Positive Skew (Right Skewed)")

# Negative Skew
ggplot(data.frame(x = -rexp(1000, rate = 1)), aes(x)) +
  geom_density(fill = "cyan", alpha = 0.5) +
  ggtitle("Negative Skew (Left Skewed)")

# Symmetrical
ggplot(data.frame(x = rnorm(1000)), aes(x)) +
  geom_density(fill = "blue", alpha = 0.5) +
  ggtitle("Zero Skewness (Symmetrical)")


```



Key Differences Between General and Sampling Distributions


----------------------------------------------------------

| **Aspect**            | **General Distributions**                                               | **Sampling Distributions**                                                     |
|------------------------|-------------------------------------------------------------------------|--------------------------------------------------------------------------------|
| **Focus**             | Distribution of raw data or random variables                           | Distribution of a statistic (e.g., sample mean, proportion)                   |
| **Population or Sample** | Describes population or a single sample                               | Derived from repeated sampling of a population                                 |
| **Examples**          | Normal, Uniform, Exponential                                           | Sampling distribution of sample mean, proportion, etc.                        |
| **Derived From**      | Directly observed data                                                 | Repeatedly calculated from samples                                            |
| **Shape**             | Depends on the data (e.g., normal, skewed)                             | Depends on sample size and population (Central Limit Theorem often applies)   |
| **Role in Statistics**| Describe the data or population characteristics                        | Used for inferential statistics (e.g., confidence intervals, hypothesis testing) |





**Example 2.12 Student Math Performance econometrics**


```{r}
#| label: example-2-10.r
data(wage1, package='wooldridge')

# Estimate log-level model
lm( log(wage) ~ educ, data=wage1 )

```